Handling String-Number Conversion in String Constraint Solving

### 2019-11-07 draft.tex
making mess

\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\sti}[1]{\mbox{\textsf{toInt}($#1$)}}
\newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
\newcommand{\cvarone}{\mbox{$V^1_{\Sigma_\epsilon}$}}
\newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
\newcommand{\modelof}[1]{[\![#1]\!]}
\newcommand{\true}{\mbox{$\mathsf{true}$}}
\newcommand{\false}{\mbox{$\mathsf{false}$}}
\newcommand{\enc}[1]{[\![#1]\!]}
%\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
\newcommand{\parikhof}[1]{\mathbb{P}{(#1)}}
\newcommand{\parikhwof}[2]{|#1|_{#2}}
\newcommand{\semof}[1]{||#1||}
\newcommand{\decode}{\mathit{decode}}
\newcommand{\pformulaof}[1]{\Phi_{#1}}

@@

An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelof{\phi_e}=\{I\mid 
I(t_1)=I(t_2)\}$. A \emph{disequality constraint} is of the form $t_1 \neq 
t_2$ and is interpreted analogously.

An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and length of a string $|x|$ for all $x \in \vars$.
%Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$. We define $\modelof{\phi}= \{I \mid (\sum_{i\in[1,n]}(j_i \times \sti{I(x_i)}+k_i\times |I(x_i)|)+ \sum_{i\in[1,m]}(l_i \times I(y_i))) \odot k \}$.
We define  $\modelof{\phi_i}= \{I \mid I(\phi_i)= \true \}$.

The \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows. For $a\in [0,9]$, we have $\sti{a}=a$ and for $s \cdot a \in [0,9]^+$, $\sti{s\cdot a} = 10\times \sti{s}+a$. For $s\notin [0,9]^+$, $\sti{s}=-1$. We define  $\modelof{\phi_s}= \{I \mid I(n)= \sti{I(x)} \}$.

A \emph{string constraint} $\phi$ is in the form of $\bigwedge_{\pi \in \Pi} \pi$, where $\Pi$ is a set of the above three kinds of constraints. We say that $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \Pi} \modelof{\pi}$ is not empty.

>>>>

\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\sti}[1]{\mbox{\textsf{toInt}($#1$)}}
\newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
\newcommand{\cvarone}{\mbox{$V^1_{\Sigma_\epsilon}$}}
\newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
\newcommand{\modelsof}[1]{[\![#1]\!]}
\newcommand{\true}{\mbox{$\mathsf{true}$}}
\newcommand{\false}{\mbox{$\mathsf{false}$}}
\newcommand{\enc}[1]{[\![#1]\!]}
%\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
\newcommand{\parikhof}[1]{\mathbb{P}{(#1)}}
\newcommand{\parikhwof}[2]{|#1|_{#2}}
\newcommand{\semof}[1]{||#1||}
\newcommand{\decode}{\mathit{decode}}
\newcommand{\pformulaof}[1]{\Phi_{#1}}

@@

An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
I(t_1)=I(t_2)\}$. A \emph{disequality constraint} is of the form $t_1 \neq 
t_2$ and is interpreted analogously.

An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and length of a string $|x|$ for all $x \in \vars$.
%Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$. We define $\modelsof{\phi}= \{I \mid (\sum_{i\in[1,n]}(j_i \times \sti{I(x_i)}+k_i\times |I(x_i)|)+ \sum_{i\in[1,m]}(l_i \times I(y_i))) \odot k \}$.
We define  $\modelsof{\phi_i}= \{I \mid I(\phi_i)= \true \}$.

The \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows. For $a\in [0,9]$, we have $\sti{a}=a$ and for $s \cdot a \in [0,9]^+$, $\sti{s\cdot a} = 10\times \sti{s}+a$. For $s\notin [0,9]^+$, $\sti{s}=-1$. We define  $\modelsof{\phi_s}= \{I \mid I(n)= \sti{I(x)} \}$.

A \emph{string constraint} $\phi$ is in the form of $\bigwedge_{\pi \in \Pi} \pi$, where $\Pi$ is a set of the above three kinds of constraints. We say that $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \Pi} \modelsof{\pi}$ is not empty.
